ps4_models

### 2020-10-30 bi-model.Rmd
whoopsies
asd

```{r}
saveRDS(model, file = "model/3chain_2k-iter_no-edu_final.rds")

# model <- readRDS("model/3chain_2k-iter_no-edu.rds")
```

@@

```{r}
table(reduced_data$state)
table(reduced_data$race_ethnicity)
table(reduced_data$age)
table(reduced_data$gender)
table(reduced_data$household_income)

table(reduced_data$vote_intention)
table(reduced_data$vote_2020)
```
```{r}
#run this for faster but similar results
model <- nnet::multinom(vote_2020 ~ state + race_ethnicity + gender +age_group,
                        data = reduced_data)
```
```{r}
testing <- data[boundary:total_rows,]
testing$vote_num <- if_else(testing$vote_2020 == "Donald Trump", 0, 1 )
# probability <- model %>% add_predicted_draws(newdata = testing)

probability <- predict(model, type = "probs", newdata = testing)
probability <- if_else(probability>0.5,1,0)

table(testing$acc)
```

@@

```{r}
levels(post_strat$age)
```

@@

@@

@@

```{r}
cleaned_post$probability <- predict(model, type = "probs", newdata = cleaned_post)
cleaned_post$probability
```

>>>>

```{r}
# saveRDS(model, file = "model/3chain_2k-iter_no-edu_final.rds")

model <- readRDS("model/3chain_2k-iter_no-edu_final.rds")
```

@@

@@

@@

cleaned_post <- cleaned_post[cleaned_post$age >= 18,]

@@

cleaned_post = cleaned_post[complete.cases(cleaned_post), ]

@@

```{r}
pred_post <- cleaned_post

pred_post <- pred_post[sample(nrow(pred_post)),]
pred_post <- pred_post[0:50000,]

probability <- predict(model, type = "response", newdata = pred_post)[,1]

```{r}
table(if_else(probability>=0.5,"Joe Biden",
                                  "Donald Trump" ))
```
